### 2015-05-21 Appendix/Appendix1.Rnw
Get rid of the dropbox working directory used in Appendix. Include data and figures to construct fully from github project.

%load packages that will be invisible on slides
<<configForMidtermAppendix, echo=FALSE, include=FALSE >>=
### Setting up R ###

setwd("C:\\Users\\Karsten\\Dropbox\\Dissertation\\CurriculumStudy\\DraftTISE\\Exams\\Exam1")
#setwd("../../../stat104/Spring2014/Exams/Exam1")
#load necessary packages
#library(productplots)
library(graphics)
library(ggplot2)
library(gridExtra)
library(reshape)
library(reshape2)
library(plyr)

versionlet <- "A"

>>>>

%load packages that will be invisible on slides
<<configForMidtermAppendix, echo=FALSE, include=FALSE >>=
### Setting up R ###
#load necessary packages
#library(productplots)
library(graphics)
library(ggplot2)
library(gridExtra)
library(reshape)
library(reshape2)
library(plyr)
